---
title: "QA Report on Vet GDP Outcomes"
author: "R(D)SVS Vet GDP Outcomes App"
date: "`r Sys.Date()`"
output:
  word_document: default
params:
  ad: null
  grad: null
  adgrad: null

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.height = 8, fig.width = 10, warning = FALSE, message = FALSE)


library(tidyverse)
library(likert)
library(grid)
library(ggstatsplot)
library(flextable)
library(officer)

set_flextable_defaults(font.size = 11, padding = 3, width = 2)
use_df_printer()


factor_sum <- function(factor_name, perc_round = 2) {
    
    x <-table(factor_name) %>% 
      as.data.frame()
    
    xx <- prop.table(table(factor_name)) %>% 
      as.data.frame() %>% 
      mutate(Perc = round((Freq*100), perc_round)) %>% 
      select(-Freq)
    
    xxx <- full_join(x,xx)
    
    
    return(xxx)
    
    
  }
  
  
  lik_hist <- function(){
    plot(likert(items = params$adgrad[,1:9], grouping = params$adgrad[,120]))
  }
  
  lik_exams <- function(){
    plot(likert(items = params$adgrad[,10:18], grouping = params$adgrad[,120]))

  }
  
  
  
  lik_prioritise_ddx <- function(){
    plot(likert(items = params$adgrad[,19:27], grouping = params$adgrad[,120]))
    
  }
  
  
  lik_tx_planning <- function(){
    plot(likert(items = params$adgrad[,28:36], grouping = params$adgrad[,120]))
  }
  
  

# l_hist <- likert(items = params$adgrad[,1:9], grouping = params$adgrad[,120])
# 
# l_exams <- likert(items = params$adgrad[,10:18], grouping = params$adgrad[,120])
# 
# l_prioritise_ddx <- likert(items = params$adgrad[,19:27], grouping = params$adgrad[,120])
# 
# l_tx_planning <- likert(items = params$adgrad[,28:36], grouping = params$adgrad[,120])
# 
# l_emergencies <- likert(items = params$adgrad[,37:42], grouping = params$adgrad[,120])
# 
# l_surg_preop <- likert(items = params$adgrad[,43:51], grouping = params$adgrad[,120])
# 
# l_surg_surg <- likert(items = params$adgrad[,52:60], grouping = params$adgrad[,120])
# 
# l_surg_postop <- likert(items = params$adgrad[,61:69], grouping = params$adgrad[,120])
# 
# l_anaesthesia <- likert(items = params$adgrad[,70:78], grouping = params$adgrad[,120])
# 
# l_pm <- likert(items = params$adgrad[,79:81], grouping = params$adgrad[,120])
# 
# l_healthcareplans <- likert(items = params$adgrad[,82:93], grouping = params$adgrad[,120])
# 
# l_epi <- likert(items = params$adgrad[,94:102], grouping = params$adgrad[,120])
# 
# l_handling <-likert(items = params$adgrad[,103:105], grouping = params$adgrad[,120])
# 
# l_evidence <- likert(items = params$adgrad[,106, drop = FALSE], grouping = params$adgrad[,120])
# 
# l_profskills <- likert(items = params$adgrad[,107:112], grouping = params$adgrad[,120])
# 
# l_preparation <- likert(items = params$adgrad[,113:119], grouping = params$adgrad[,120])

```


# 2022 Graduate and VetGDP Adviser Surveys
## About this report

This report was generated based on the Royal College of Veterinary Surgeons (RCVS) Education Outcomes Data from Graduates and Advisers received in 2023. It was generated from the full redacted data provided by the RCVS for the purposes of additional analyses for quality improvement and processed via the R(D)SVS app. [More information about the app can be found here](https://github.com/jillymackay/VSC_2023_VetGDP).

This data was collected by the RCVS, and the R(D)SVS app has no input into question formation or data collection. 

Graduates respond to the RCVS survey prior to setting up their personal e-portfolio. Advisers were matched with graduates to act as a mentor and asked to complete the survey  approximately 6 weeks after the graduate had started their programme to allow time for skills to be assessed. Advisers worked only with 2022 graduates. 

**Please note**: While we have data from graduates and data from advisers, we do not have paired data, e.g. we do not know which adviser was linked with what graduate. This limits the inferences and statistical comparisons that can be made. For example, we may see that for a given skill, the advisers have a lower average graduate preparedness score than the graduates do. There are two possible explanations for this finding. The first is that all advisers tend to rate their graduates a few points lower than the graduate's rate themselves. In this case there would be a consistent effect where all graduates are less prepared than they believe. The second explanation is that most advisers and graduates agree, but there are some where there is a very large mismatch between graduate and adviser. In this case, the effect is constrained to certain cases. With the current data we cannot distinguish between these two plausible explanations.


The majority of questions within the survey are presented in the following format: 

> How well prepared was the graduate to [conduct skill] at the point of graduation?

> \1. (Not at all prepared)

> \2.

> \3.

> \4.

> \5. (Completely prepared)



There are 105 clinical skill related questions and 14 professional skill related questions. Graduates were also asked to rate their overall confidence to work independently when starting their first role on a scale from 1 (Not at all confident) to 5 (Extremely confident).


# Adviser and Graduate Role

While it is possible for advisers and graduates to work in a range of areas, the graduates first roles and the adviser areas in your data are presented below. 


### Advisers
```{r}
factor_sum(params$ad$`Adviser Area`) %>% 
  rename("Adviser Area" = factor_name,
         "Frequency" = Freq,
         "Percentage" = Perc) %>% 
  arrange(Percentage) %>% 
  flextable() %>% 
  set_caption("Frequency and proportion of adviser area")

```

### Graduates
```{r}
factor_sum(params$grad$`Grad First Role`) %>% 
  rename("Graduate First Role" = factor_name,
         "Frequency" = Freq,
         "Percentage" = Perc) %>%
  arrange(Percentage) %>% 
  flextable() %>% 
  set_caption("Frequency and proportion of graduate first role")

```

## Non applicable responses

Within the adviser data there is a large number of 'Not Applicable' responses to the 105 questions asking about the graduate's preparedness to practice a given clinical skill. It is expected that the Not Applicable adviser responses come from advisers who were not able to assess the graduate on a skill, either because they worked wholly within Small Animal practice, or perhaps because they did not feel able to assess the graduate on this skill for another reason. For some questions, the majority of advisers were not able to rate their graduates, see below.


```{r}
params$adgrad %>% 
  pivot_longer(cols= c(-grp), names_to = "response", values_to = "score" ) %>% 
  filter(is.na(score)) %>% 
  group_by(grp, response, score) %>% 
  tally() %>%
  mutate("Percentage" = round(n/78*100, 2)) %>% 
  rename("Group" = grp,
         Question = "response") %>% 
  select(Group, Question, n, Percentage) %>% 
  arrange(Percentage) %>% 
  flextable() %>% 
  set_caption("Frequency of NA responses across advisers.\nNote, graduates unlikely to record an 'NA' response for any question")

```



# Graduate Data

Graduate gender, age, ethnicity and disability states were self-reported and as below. 

**Gender**
```{r}
factor_sum(params$grad$`Grad Gender`)  %>% 
  rename("Graduate Gender" = factor_name,
         "Frequency" = Freq,
         "Percentage" = Perc) %>%
  flextable() %>% 
  set_caption("Graduate gender")
```

**Age**
```{r}
factor_sum(params$grad$`Grad Age`) %>% 
  rename("Graduate Age" = factor_name,
         "Frequency" = Freq,
         "Percentage" = Perc) %>%
  flextable() %>% 
  set_caption("Graduate age category")

```

**Ethnicity**
```{r}
factor_sum(params$grad$`Grad Ethnicity`) %>% 
  rename("Graduate Ethnicity" = factor_name,
         "Frequency" = Freq,
         "Percentage" = Perc) %>%
  flextable() %>% 
  set_caption("Graduate ethnicity")
```

**Disability**
```{r}
factor_sum(params$grad$`Grad Disability`) %>% 
  rename("Graduate disability status" = factor_name,
         "Frequency" = Freq,
         "Percentage" = Perc) %>%
  flextable() %>% 
  set_caption("Graduate disability recording")

```


Graduates were asked to rate their confidence from 1 (Not at all confident) to 5 (Extremely confident) to work independently when they started their first role:

```{r, fig.cap = "Graduate's rating of their own confidence at start of employment", fig.height = 6, fig.width = 10}
params$grad %>%
  ggplot(aes(x = `Grad Confidence First Start`, fill = `Grad First Role`)) +
  geom_bar() +
  theme_classic() +
  scale_x_continuous(breaks = seq(1, 5, 1), limits = c(0,5.5)) +
  labs(y = "Count of Graduates")

```



# Adviser Data

Adviser age, gender, and their position were provided. 


*Age*
```{r}

factor_sum(params$ad$`Adviser Age`) %>% 
    rename("Adviser Age" = factor_name,
         "Frequency" = Freq,
         "Percentage" = Perc) %>% 
  flextable() %>% 
  set_caption("Adviser age groups")
```

*Gender*
```{r }
factor_sum(params$ad$`Adviser Gender`) %>% 
    rename("Adviser Gender" = factor_name,
         "Frequency" = Freq,
         "Percentage" = Perc) %>% 
  flextable() %>% 
  set_caption("Adviser gender")
```

*Position*
```{r}
factor_sum(params$ad$`Adviser Position`) %>% 
    rename("Adviser Position" = factor_name,
         "Frequency" = Freq,
         "Percentage" = Perc) %>% 
  flextable() %>% 
  set_caption("Adviser position")
```



# Comparisons of Grad vs Adviser Perspectives

It may be useful to explore where there were differences between the adviser and graduate ratings of preparedness. Note, as previously mentioned, we cannot determine whether these differences are a consistent disagreement between advisers and graduates, or whether it is a large disagreement in a select number of cases. 

Additionally, please note that there are a number of 'NA' responses for advisers. These are not pictured here, please refer to the table above for a note of how many NA responses are contained within each category. 



```{r, fig.cap = "History taking\n(1 (Not at all prepared), 5 (Completely prepared))", fig.height = 10, fig.width = 10}

lik_hist()

```


<!-- ```{r, fig.cap =  "Examinations\n(1 (Not at all prepared), 5 (Completely prepared))", fig.height = 10, fig.width = 10} -->
<!-- plot(l_exams)  -->
<!-- ``` -->

<!-- ```{r, fig.cap= "Prioritise a differential diagnosis\n(1 (Not at all prepared), 5 (Completely prepared))", fig.height = 10, fig.width = 10} -->
<!-- plot(l_prioritise_ddx)  -->
<!-- ``` -->

<!-- ```{r, fig.cap = "Treatment planning\n(1 (Not at all prepared), 5 (Completely prepared))", fig.height = 10, fig.width = 10} -->
<!-- plot(l_tx_planning)  -->
<!-- ``` -->


<!-- ```{r, fig.cap = "Emergencies\n(1 (Not at all prepared), 5 (Completely prepared))", fig.height = 10, fig.width = 10} -->
<!-- plot(l_emergencies) -->
<!-- ``` -->


<!-- ```{r, fig.cap = "Surgery (pre-op prep)\n(1 (Not at all prepared), 5 (Completely prepared))", fig.height = 10, fig.width = 10} -->
<!-- plot(l_surg_preop) -->
<!-- ``` -->

<!-- ```{r, fig.cap = "Surgery\n(1 (Not at all prepared), 5 (Completely prepared))", fig.height = 10, fig.width = 10} -->
<!-- plot(l_surg_surg) -->
<!-- ``` -->


<!-- ```{r, fig.cap = "Surgery (post op care)\n(1 (Not at all prepared), 5 (Completely prepared))", fig.height = 10, fig.width = 10} -->
<!-- plot(l_surg_postop) -->
<!-- ``` -->


<!-- ```{r, fig.cap = "Anaesthesia\n(1 (Not at all prepared), 5 (Completely prepared))", fig.height = 10, fig.width = 10} -->
<!-- plot(l_anaesthesia) -->
<!-- ``` -->


<!-- ```{r, fig.cap = "Post-mortem\n(1 (Not at all prepared), 5 (Completely prepared))"} -->
<!-- plot(l_pm) -->
<!-- ``` -->


<!-- ```{r, fig.cap = "Preventative healthcare plans\n(1 (Not at all prepared), 5 (Completely prepared))", fig.height = 10, fig.width = 10} -->
<!-- plot(l_healthcareplans) -->
<!-- ``` -->

<!-- ```{r, fig.cap ="Basic epidemiological investigations\n(1 (Not at all prepared), 5 (Completely prepared))", fig.height = 10, fig.width = 10} -->
<!-- plot(l_epi) -->
<!-- ``` -->


<!-- ```{r, fig.cap = "Animal handling\n(1 (Not at all prepared), 5 (Completely prepared))"} -->
<!-- plot(l_handling) -->
<!-- ``` -->

<!-- ```{r, fig.cap = "Evaluating evidence\n(1 (Not at all prepared), 5 (Completely prepared))"} -->
<!-- plot(l_evidence) -->
<!-- ``` -->



<!-- ```{r, fig.cap = "Professional skills and attributes required for independent practice\n(1 (Not at all prepared), 5 (Completely prepared))", fig.height = 10, fig.width = 10} -->
<!-- plot(l_profskills) -->
<!-- ``` -->


<!-- ```{r, fig.cap = "Professional skills and attributes at the point of graduation\n(1 (Not at all prepared), 5 (Completely prepared))", fig.height = 10, fig.width = 10} -->
<!-- plot(l_preparation) -->
<!-- ``` -->

